---
title: "Technical variations in the Latarjet procedure impact glenohumeral joint stability: A simulation study"
author:
  - name: Aaron S. Fox
    affiliation: Centre for Sports Research,Barwon Centre for Orthopaedic Research and Education (B-CORE)
    footnote: 1
  - name: Stephen D. Gill
    affiliation: Barwon Centre for Orthopaedic Research and Education (B-CORE),School of Medicine,Orthopaedic Department
  - name: Jason Bonacci
    affiliation: Centre for Sports Research
  - name: Richard S. Page
    affiliation: Barwon Centre for Orthopaedic Research and Education (B-CORE),School of Medicine,Orthopaedic Department
address:
  - code: Centre for Sports Research
    address: Centre for Sports Research, School of Exercise and Nutrition Sciences, Deakin University, Geelong, Australia
  - code: Barwon Centre for Orthopaedic Research and Education (B-CORE)
    address: Barwon Centre for Orthopaedic Research and Education (B-CORE), Barwon Health, St John of Jod Hospital and Deakin University, Geelong, Australia
  - code: School of Medicine
    address: School of Medicine, Deakin University, Geelong, Australia
  - code: Orthopaedic Department
    address: Orthopaedic Department, University Hospital Geelong, Barwon Health, Geelong, Australia
footnote:
  - code: 1
    text: "Corresponding Author: aaron.f@deakin.edu.au"
abstract: |
  Insert abstract...

journal: BioR$\chi$iv
date: "Version 1.0; Last Updated:`r Sys.Date()`"
bibliography: mybibfile.bib
#linenumbers: true
numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

#Multiple knit options - in YAML
# knit: (function(inputFile, encoding) {
#   rmarkdown::render(inputFile, encoding = encoding,
#   output_format = "all") })


```

# Introduction

Shoulder instability injuries occur with excessive force that translates the humeral head out of the shoulder joint socket [@Thangarajah2016]. Shoulder instability injuries are a concerning problem affecting young athletes in overhead collision sports (e.g. Australian football; rugby) [@Bohu2015,@Orchard2013]. Effective clinical care is vital to avoid recurrent injuries, as well as reduced shoulder function and joint degradation [@Thangarajah2016]. Surgery is commonly used to address pathology, restore function, and correct stability [@Kavaja2012]. The Latarjet procedure is a non-anatomic, open shoulder reconstruction surgery involving a bone block via transfer of the coracoid process to the anterior glenoid (i.e. coracoid bone graft) with the attached conjoint tendon [@Latarjet1954]. The Latarjet procedure is commonly used in cases with significant glenoid bone loss, large humerus compression fractures, or glenoid and humeral bone defects [@Millett2005] — and is effective in combatting recurrent anterior instability injury [@Bonacci2018,@Bessiere2014]. While it is a more aggressive treatment, open Latarjet surgeries are emerging as the preferred option for shoulder stabilisation, especially in contact sport settings [@Millett2005,@Bonazza2017].

The Latarjet procedure requires high precision, and subtle variations in surgical technique may impact the likelihood of joint instability and subsequent injury [@Bhatia2014,@Ghodadra2010].

# Methods

- All the different simulation iterations take too long, need to reduce
- If we do 1 Bankart defect (e.g. 37.5% glenoid width radius), 1 Hill-Sachs defect (e.g. 31% humeral head diameter) in isolation and combination; at one elevation and external rotation position; in 3, 4 and 5 o clock directions — that will be a total of 4 defect simulations x 3 direction (i.e. 12 simulations) multiplied by the different Latarjet variations. Based on 20 minute simulations this would take 4 hours to get through each. Are the different translation directions needed?
- The Bankart defect and Hill-Sachs lesion sizes chosen, along with the elevation and external rotation positions can be referred to existing literature (Walia et al. studies, Kaar et al. Itoi et al.) as identified for significantly reducing joint stability. External rotation of 40 degrees might align with maximum achievable for Latarjet operated patients too?


- Use distance to dislocation as our primary metric then we can compare how the presence of a bone defect affects the distance relative to the intact glenoid (i.e. as a %)
- We can then apply this same approach to testing how completing the Latarjet procedure changes the distance, still probably keeping this in the same relative scale to the intact model (i.e. does it get back to 100%, or how close to intact does the Latarjet get to).
- We can then look at the data across Latarjet variations (i.e. displacement in the vertical and horizontal directions, graft size) in isolation and see what impact this has. From a practical perspective, this might tell us where the optimal positioning is to maximise distance to dislocation; whether larger grafts equate to better outcomes; whether a smaller graft can be used with optimum placement; whether you need bigger grafts if you stray away from optimum placement etc. Examining the results from the individual variations in the context of one another, given they are on the same proportional scale, should theoretically help answer these questions. 
- It’s also possible that the above mentioned aspects may vary with different bone defect sizes or types (e.g. Hill-Sachs included?)


``` {r cars}

#Test some r code
summary(cars)

```





Bibliography styles
===================

There are various bibliography styles available. You can select the
style of your choice in the preamble of this document. These styles are
Elsevier styles based on standard styles like Harvard and Vancouver.
Please use BibTeX to generate your bibliography and include DOIs
whenever available.



References {#references .unnumbered}
==========
